---
title: "Curve fit results"
author: "Emil Bjerglund Pedersen"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Curve fit results}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

Raman data can be tedious to import and analyse, when exported from Renishaw Wire. I found myself writing similar pieces of code over an over, to solve the same problems and have collected it all in this R package for easy use. This document will demonstrate how to work with **curve fit results**. Another vignette is available describing functions for [spectral maps](spectral_maps.html).

## Importing data

Curve fit results from wire can be exported to a set of `.txt` files. The files should be saved indicating the peak and corresponding feature, e.g. `2D FWHM.txt` for the Full-width at Half-max of the 2D peak (use `int` for intensity and `pos` for position).

The package includes some sample data that will be used for demonstration purposes. `cf_folder` should point to the folder containing your curve fit results. 

```{r, message=FALSE}
library(tidyverse)
library(gRaphene)

cf_folder <- system.file("extdata/graphene_curve_fit_export", package = "gRaphene")
data_cf <- gr_cf_read(cf_folder)
```

Common graphene ratios (`D/G`, `2D/G` and `D/Dp`) will automatically be calculated if the right peaks are present.

## Summary statistics
The data can be summarised easily by using `gr_cf_summary(data_cf)`. The example used here contains a mix of SiO2 and graphene flakes, so in some cases i use `filter()` or `mutate()` to deal with values that are outside the expected ranges.

```{r}
data_cf_filtered <- data_cf %>% filter(`G int` > 50) %>% select(-starts_with('SiO2'))

knitr::kable(
  gr_cf_summary(data_cf_filtered), 
  digits = c(0, 1, 0, 1, 1, 0, 1, 1, 0, 1, 2, 2)
)
```


## Plotting curve fits
Getting an overview of the data from curve-fits can be challenging. The `gr_cf_plot` accepts a data-frame with columns `x`, `y` and a `value` and plots a map. Arguments can be passed to change appearance of the plot and size of the scalebar. See available color schemes by running the command `RColorBrewer::display.brewer.all()`. 

```{r, fig.show='hold'}
data_cf_small <- data_cf %>% select(x, y, `G int`) %>% rename(value = `G int`)
gr_cf_plot(df = data_cf_small, name = 'G int')
gr_cf_plot(df = data_cf_small, name = 'G int', scalebar = 2, palette = "Greys")
```

 A whole range of maps can be plotted by supplying a data-frame to `gr_cf_plot_all()` as in the following example. This function also accepts the `scalebar` and `palette` arguments.

```{r, fig.width = 7, fig.height=8}
data_cf %>%
  mutate(condition = `G int` > 50) %>% 
  mutate(`2D FWHM` = ifelse(condition, `2D FWHM`, NA)) %>% 
  mutate(`D FWHM` = ifelse(condition, `D FWHM`, NA)) %>%  
  mutate(`G FWHM` = ifelse(condition, `G FWHM`, NA)) %>%  
  mutate(`D/G-ratio` = ifelse(condition, `D/G-ratio`, NA)) %>%
  mutate(`2D/G-ratio` = ifelse(condition, `2D/G-ratio`, NA)) %>% 
  gr_cf_plot_all()
```


## Plotting curve-fitted spectra

In some cases it is desireable to present the results of a curve-fit on a spectrum as an example. This is possible using `gr_cf_fit_add()` and `gr_cf_fit_plot()`. It is necessary to have two files: 

1. A spectrum in a tab-separated text file (as exported by Wire) containing columns with wavenumber and intensity. 
2. A text-file with Curve fit results, which is also exported from Wire by right-clicking the results-table after a curve fit and choosing 'Copy Results'.

```{r, fig.width = 7, fig.height=3, message=FALSE}
curvefit <- system.file("extdata/curvefit_data.txt", package = "gRaphene")
spectrum <- system.file("extdata/spectrum_example.txt", package = "gRaphene")

gr_cf_fit_plot(spectrum, curvefit)
```

The object returned by `gr_cf_fit_plot()` is an ordinary ggplot2 object, and can be modified by adding new layers.

```{r, fig.width = 7, fig.height=3, message=FALSE}
gr_cf_ann <- gr_cf_fit_add(spectrum, curvefit) %>% 
  select(-intensity, -envelope) %>% 
  gather(key = "peak", value = "intensity", -wavenumber) %>% 
  group_by(peak) %>% 
  filter(intensity == max(intensity))

gr_cf_fit_plot(spectrum, curvefit) +
  ggthemes::theme_few() +
  theme(axis.title.y = element_blank(),
        axis.text.y = element_blank(),
        axis.ticks.y = element_blank(),
        legend.position = "none") +
  scale_fill_brewer(palette = "Set3", guide = guide_legend(nrow = 1)) +
  geom_text(data = gr_cf_ann, aes(x = wavenumber, y = intensity, label = peak), nudge_y = 40, nudge_x = 10)
```

Finally, if you wish to generate your completely own plot, just use `gr_cf_fit_add()` to generate the fitted data, and plot it manually.

```{r, message=FALSE}
fit_data <- gr_cf_fit_add(spectrum, curvefit)

knitr::kable(head(fit_data, 5), digits = 3)
```

